Titeln på avhandlingens språk

### 2023-03-04 publications/2023EdgeDroid2/appendices.tex

\appendix{}\label[appendixwithoutnumber]{appx1}
% \subsection*{Sampling optimisation}

@@

We first borrow the idea of checkpointing density from~\cite{Satoshi1992Optimal} and define an instantaneous sampling rate function $r(t)$ which is related to $\{t_n\}$ such that,
\begin{alignat}{1}
{\int_{t_{n-1}}^{t_n}}r(t)\dif t=1,\;\forall n\geq1\label{rt}
\end{alignat}
Note that, for periodic sampling, this function is a constant, equal to the sampling frequency.
In the aperiodic case, we find $r^*(t)$, the $r(t)$ that minimizes $\mathcal{E}$.
By construction, the number of samples taken up to any time instant can be computed directly by computing the area under $r(t)$.
Thus, we obtain the expected number of samples $\mathbb{E}[\mathcal{S}]$ as
\begin{alignat}{1}
\mathbb{E}[\mathcal{S}]&=\int_{t=0}^{\infty}\bigg(\!\int_{x=0}^{t}\!\!\!\!r(x)\,\mathrm{d}x\bigg)f_{\mathcal{T}}(t)\,\mathrm{d}t.\label{Es}
\end{alignat}

@@

As per the Euler-Lagrange equation from the calculus of variations~\cite{Bellman1954Dynamic,Arfken2015Calculus}, the extreme value of $\mathcal{E}$ is obtained at 
\begin{alignat}{1}
r^*(t)&=\sqrt{\dfrac{\beta f_\mathcal{T}(t)}{2\alpha\bar{F}_\mathcal{T}(t)}}.\\
\intertext{Thus, for a Rayleigh distributed $\mathcal{T}$ with parameter $\sigma$,}
r^*(t)&=\sqrt{\dfrac{\beta t}{2\alpha\sigma^2}}\\
\Rightarrow &\int_{t_n}^{t_{n+1}}\!\!\!\sqrt{\dfrac{\beta t}{2\alpha\sigma^2}}\,\mathrm{d}t=1,\;\forall n\geq1\nonumber\tag{from \eqref{rt}}\\
\Rightarrow &\;t_{n+1}^{\frac{3}{2}}-t_{n}^{\frac{3}{2}}=3\sigma\!\sqrt{\tfrac{\alpha}{2\beta}}\nonumber\\
\intertext{We have $t_0=0$. Substituting $n=1,2,\dots$, in order, in the above equation provides us our final result}
&\;t_n=\Big(3\sigma\!\sqrt{\tfrac{\alpha}{2\beta}}\Big)^{\frac{2}{3}}n^{\frac{2}{3}}\label{tnRayleigh}.
x\end{alignat}
% Note that throughout the paper we use a exGaussian distribution but not Rayleigh. This is because, 
Note that, due to the close similarity in their density functions, the task times can be approximated fairly equally to an \gls{exGaussian} distribution as well as a Rayleigh distribution, with the former attracting more attention from works like~\cite{Rohrer1994analysis,Palmer2011shapes,Marmolejo2022generalised}.
This is the reason why the above results are applicable in this work where we have predominantly considered \gls{exGaussian} distribution.
Furthermore, we have also verified the closeness of the results as well as the validity of the approximations made in the proofs using distribution fitting and simulations.

>>>>

%\appendix{}
\section{Appendix}\label[appendixwithoutnumber]{appx1}
% \subsection*{Sampling optimisation}

@@

We first borrow the idea of checkpointing density from~\cite{satoshi1992optimal} and define an instantaneous sampling rate function $r(t)$ which is related to $\{t_n\}$ such that,
\begin{alignat}{1}
{\int_{t_{n-1}}^{t_n}}r(t)\dif t=1,\;\forall n\geq1\label{rt}
\end{alignat}
Note that, for periodic sampling, this function is a constant, equal to the sampling frequency.
In the aperiodic case, we find $r^*(t)$, the $r(t)$ that minimizes $\mathcal{E}$.
By construction, the number of samples taken up to any time instant can be computed directly by computing the area under $r(t)$.
Thus, we obtain the expected number of samples $\mathbb{E}[\mathcal{S}]$ as
\begin{alignat}{1}
\mathbb{E}[\mathcal{S}]&=\int_{t=0}^{\infty}\bigg(\!\int_{x=0}^{t}\!\!\!\!r(x)\,\mathrm{d}x\bigg)f_{\mathcal{T}}(t)\,\mathrm{d}t.\label{Es}
\end{alignat}

@@

As per the Euler-Lagrange equation from the calculus of variations~\cite{bellman1954dynamic,arfken2013calculus}, the extreme value of $\mathcal{E}$ is obtained at
\begin{alignat}{1}
r^*(t)&=\sqrt{\dfrac{\beta f_\mathcal{T}(t)}{2\alpha\bar{F}_\mathcal{T}(t)}}.\\
\intertext{Thus, for a Rayleigh distributed $\mathcal{T}$ with parameter $\sigma$,}
r^*(t)&=\sqrt{\dfrac{\beta t}{2\alpha\sigma^2}}\\
\Rightarrow &\int_{t_n}^{t_{n+1}}\!\!\!\sqrt{\dfrac{\beta t}{2\alpha\sigma^2}}\,\mathrm{d}t=1,\;\forall n\geq1\nonumber\tag{from \eqref{rt}}\\
\Rightarrow &\;t_{n+1}^{\frac{3}{2}}-t_{n}^{\frac{3}{2}}=3\sigma\!\sqrt{\tfrac{\alpha}{2\beta}}\nonumber\\
\intertext{We have $t_0=0$. Substituting $n=1,2,\dots$, in order, in the above equation provides us our final result}
&\;t_n=\Big(3\sigma\!\sqrt{\tfrac{\alpha}{2\beta}}\Big)^{\frac{2}{3}}n^{\frac{2}{3}}\label{tnRayleigh}.
x\end{alignat}
% Note that throughout the paper we use a exGaussian distribution but not Rayleigh. This is because, 
Note that, due to the close similarity in their density functions, the task times can be approximated fairly equally to an \gls{exGaussian} distribution as well as a Rayleigh distribution, with the former attracting more attention from works like~\cite{rohrer1994analysis,palmer2011what,marmolejo_ramos2022generalised}.
This is the reason why the above results are applicable in this work where we have predominantly considered \gls{exGaussian} distribution.
Furthermore, we have also verified the closeness of the results as well as the validity of the approximations made in the proofs using distribution fitting and simulations.

### 2023-03-04 publications/2023EdgeDroid2/conclusion.tex

This paper addresses the difficulty of benchmarking \gls{WCA} by offering a model-based alternative to the extensive human-user studies that would otherwise be required.
It first introduces the \edgedroid{} model of human timing behavior for \gls{WCA}.
This model represents a stochastic approach to execution time modeling which builds upon prior data~\cite{olguinmunoz:impact2021}.
It further introduces a novel procedure for the generation of synthetic traces of frames in step-based \gls{WCA}, allowing for a full end-to-end emulation of a human when combined with the timing model.

@@

This work serves as an important, yet initial step towards realistic modeling of human behavior in \gls{WCA}, and more generally \gls{AR}.
Many directions remain open to additional exploration in this space.
For instance, our current model only targets a particular class of step-based \gls{WCA}, and extension of our methodology to other classes of these applications, or even more generally to \gls{AR} and \gls{XR}, is on our roadmap.
Our data~\cite{olguinmunoz:impact2021} also only considers young undergraduate students at a highly competitive university in the United States.
An extension of this dataset and the model towards a more representative sample of the general population would surely be a valuable endeavor.
Corresponding research is needed to determine individual difference factors that would substantially impact response to \gls{WCA} in novel populations.

>>>>

This paper addresses the difficulty of benchmarking \gls{WCA} by offering a model-based alternative to the extensive human-user studies that would otherwise be required.
It first introduces the \edgedroid{} model of human timing behavior for \gls{WCA}.
This model represents a stochastic approach to execution time modeling which builds upon prior data~\cite{olguinmunoz2021impact}.
It further introduces a novel procedure for the generation of synthetic traces of frames in step-based \gls{WCA}, allowing for a full end-to-end emulation of a human when combined with the timing model.

@@

This work serves as an important, yet initial step towards realistic modeling of human behavior in \gls{WCA}, and more generally \gls{AR}.
Many directions remain open to additional exploration in this space.
For instance, our current model only targets a particular class of step-based \gls{WCA}, and extension of our methodology to other classes of these applications, or even more generally to \gls{AR} and \gls{XR}, is on our roadmap.
Our data~\cite{olguinmunoz2021impact} also only considers young undergraduate students at a highly competitive university in the United States.
An extension of this dataset and the model towards a more representative sample of the general population would surely be a valuable endeavor.
Corresponding research is needed to determine individual difference factors that would substantially impact response to \gls{WCA} in novel populations.

### 2023-03-04 publications/2023EdgeDroid2/implications_optimization.tex

\begin{figure*}
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/sampling_optimization.png}
        \caption{%
            Round-trip time versus mean number of captured samples per step, averaged over all \num{100} repetitions of the experiment.
            Note the logarithmic scale on the vertical axis.
            Error bars indicate \SI{95}{\percent} \glspl{CI}.
        }
    \end{subfigure}\\
    \medskip
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/sampling_optimization_diff.png}
        \caption{%
            Percentage difference in mean number of captured samples per step by the sample-count-optimized approach with respect to the three reference schemes.
            In other words, curves represent the relative performance of the sample-count-optimized scheme when using the corresponding reference scheme as baseline.
            Error bars indicate \SI{95}{\percent} \glspl{CI}, calculated using a two-sided t-test.
        }
    \end{subfigure}
    \caption{%
        Summary of results for experiment comparing the sample-count-optimized aperiodic sampling scheme to the reference schemes and \textcite{wang2019towards}'s \gls{CDF}-based approach.
    }\label{fig:optimization:samples}
\end{figure*}

@@

\begin{figure*}
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/energy_optimization.png}
        \caption{%
            Round-trip time versus mean per step energy consumption, averaged over all \num{100} repetitions of the experiment.
            Error bars indicate \SI{95}{\percent} \glspl{CI}.
        }
    \end{subfigure}\\
    \medskip
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/energy_optimization_diff.png}
        \caption{%
            Percentage difference in mean per step energy consumption by the energy-optimized sampling scheme with respect to the three reference schemes.
            Error bars indicate \SI{95}{\percent} \glspl{CI}, calculated using a two-sided t-test.
        }
    \end{subfigure}
    \caption{%
        Summary of results for experiment comparing the energy-optimized aperiodic sampling scheme to the reference schemes and \textcite{wang2019towards}'s \gls{CDF}-based approach.
    }\label{fig:optimization:energy}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/sampling_optimization.png}
        \caption{%
            Round-trip time versus mean number of captured samples per step, averaged over all \num{100} repetitions of the experiment.
            Note the logarithmic scale on the vertical axis.
            Error bars indicate \SI{95}{\percent} \glspl{CI}.
        }
    \end{subfigure}\\
    \medskip
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/sampling_optimization_diff.png}
        \caption{%
            Percentage difference in mean number of captured samples per step by the sample-count-optimized approach with respect to the three reference schemes.
            In other words, curves represent the relative performance of the sample-count-optimized scheme when using the corresponding reference scheme as baseline.
            Error bars indicate \SI{95}{\percent} \glspl{CI}, calculated using a two-sided t-test.
        }
    \end{subfigure}
    \caption{%
        Summary of results for experiment comparing the sample-count-optimized aperiodic sampling scheme to the reference schemes and \textcite{wang2019towards}'s \gls{CDF}-based approach.
    }\label{fig:optimization:samples}
\end{figure*}

@@

\begin{figure*}
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/energy_optimization.png}
        \caption{%
            Round-trip time versus mean per step energy consumption, averaged over all \num{100} repetitions of the experiment.
            Error bars indicate \SI{95}{\percent} \glspl{CI}.
        }
    \end{subfigure}\\
    \medskip
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/energy_optimization_diff.png}
        \caption{%
            Percentage difference in mean per step energy consumption by the energy-optimized sampling scheme with respect to the three reference schemes.
            Error bars indicate \SI{95}{\percent} \glspl{CI}, calculated using a two-sided t-test.
        }
    \end{subfigure}
    \caption{%
        Summary of results for experiment comparing the energy-optimized aperiodic sampling scheme to the reference schemes and \textcite{wang2019towards}'s \gls{CDF}-based approach.
    }\label{fig:optimization:energy}
\end{figure*}

### 2023-03-04 publications/2023EdgeDroid2/optimization_framework.tex

%\appendix{}
\section{Appendix}\label[appendixwithoutnumber]{appx1}
% \subsection*{Sampling optimisation}

In this appendix, we give the mathematical derivation of the optimum aperiodic sampling interval discussed in \cref{ssec:optframework}.
We start with the general solution, where the objective function to be minimized is given by \cref{eq:epsilon_terminal}:
\begin{alignat}{1}
    \Rightarrow\mathcal{E}&=\alpha\mathbb{E}[\mathcal{S}]+\beta\mathbb{E}[\mathcal{W}]+C\nonumber
\end{alignat}

>>>>

\section{An optimization framework for \gls{WCA}}\label{sec:optframework}

Our optimization approach focuses on the individual steps which comprise a complete \gls{WCA} task.
Thus, we begin by assuming a given execution time distribution \( \mathcal{T} \), and take the modeling and partial solution approach from recents works on energy efficient sampling in edge-based feedback systems.
In \textcite{moothedath2021energy,moothedath2022energy1}, the authors model the energy in terms of the expected number of samples $\mathbb{E}[\mathcal{S}]$ and the expected wait time $\mathbb{E}[\mathcal{W}]$ experienced by the user.
The authors then find the optimum periodic sampling interval that minimizes this energy, or equivalently the non-constant parts of this energy termed as \textit{Energy Penalty}.

% In this optimization, the constant parts are excluded as it does not affect the process.
With a value much smaller than the execution time of the event, the \gls{RTT} of the final sample is included in this constant part, which is why $\mathcal{W}$ is computed without it.
Next, in~\cite{moothedath2022energy2}, the author retains the model and removes the constraint of periodicity to find the optimum aperiodic sampling instants $\{t_n,\,n=1,2,\dots\}$ that minimize the same energy penalty.

In this work, we use the modeling from~\cite{moothedath2022energy2} to find the optimum \emph{aperiodic} sampling interval.
However, instead of using their two-step approach to find the solution which includes a recursive solution followed by a bisection algorithm, we develop a novel, approximate, but easier solution to finding the set of the optimum aperiodic sampling intervals.
Furthermore, instead of directly optimizing for energy, we start by noting that, in general, any objective metric in these applications which relates to sampling and the responsiveness of the system will present itself
% that an objective metric of a variety of optimization problems that are related to sampling, RTT, responsiveness or wait time present themselves
% % in a format similar to that of the energy,
as a linear combination between $\mathbb{E}[\mathcal{S}]$ and $\mathbb{E}[\mathcal{W}]$ plus terms independent of the number of samples or wait time.
Let $\mathcal{E}$ correspond to such an objective metric.
Thus,
\begin{alignat}{1}
    \Rightarrow\mathcal{E}&=\alpha\mathbb{E}[\mathcal{S}]+\beta\mathbb{E}[\mathcal{W}]+C\;\label{eq:epsilon_terminal}
\end{alignat}

% This corresponds to a Lagrangian function of this optimization, with \ensuremath{\frac{\alpha}{\beta}} representing the Lagrangian parameter.
Here, $\alpha, \beta$ and $C$ are constants responsible for modifying the objective function from one metric to another.
For instance, in the modeling used by~\cite{moothedath2021energy,moothedath2022energy1,moothedath2022energy2}, the chosen characterization results in a metric which is equal to the energy penalty.
Our solution which minimizes \cref{eq:epsilon_terminal} is provided in \cref{tn_approx_rayleigh}.
It assumes a $\mathcal{T}$ distributed according to a Rayleigh distribution with parameter $\sigma$.
The complete mathematical derivation that leads to this formula is detailed in \cref{appx1}.

\begin{alignat}{1}
% r^*(t)&=\sqrt{\dfrac{\beta t}{2\alpha\sigma^2}}\nonumber\\
% \Rightarrow
    t_n&=\Big(3\sigma\!\sqrt{\tfrac{\alpha}{2\beta}}\Big)^{\frac{2}{3}}n^{\frac{2}{3}}\label{tn_approx_rayleigh}
\end{alignat}

We start with the general solution, where the objective function to be minimized is given by \cref{eq:epsilon_terminal}:
\begin{alignat}{1}
    \Rightarrow\mathcal{E}&=\alpha\mathbb{E}[\mathcal{S}]+\beta\mathbb{E}[\mathcal{W}]+C\nonumber
\end{alignat}

### 2023-03-04 publications/2023EdgeDroid2/related_work.tex

There exist a number of approaches to the characterization and benchmarking of mobile \gls{XR}, and by extension \gls{WCA}, deployments.
\emph{OpenRTiST}~\cite{george2020openrtist} is a tool which uses a compute-heavy, yet latency-sensitive workload --- image style transfer~\cite{jing2019neural} --- to load and benchmark edge computing deployments.
It acts as an end-to-end realistic \gls{AR} workload, allowing thus researchers to measure the real end-to-end latencies of such systems.
\textcite{Chen2017Empirical} use a number of prototype \gls{WCA} implementation to study and characterize real-world latency bounds in these systems.
In~\cite{lecci2021open}, the authors collect and analyze large amounts of \gls{VR} network traffic, which they then use to construct a synthetic model for the generation of traces of such traffic.
\textcite{chetoui2022arbench} propose \emph{ARBench}, a toolkit for the benchmarking of mobile hardware in the context of \gls{AR}.
The toolkit incorporates a series of workloads which stress different components of the mobile device and calculates a score for each workload.
\emph{Yahoo Cloud Serving Benchmark}~\cite{cooper2010benchmarking} and \emph{DCBench}~\cite{jia2013characterizing} are workload sets intended for benchmarking cloud services which have further been used in the context of benchmarking edge computing infrastructure for \gls{AR} suitability.
\emph{Edgebench}~\cite{das2018edgebench} and \emph{Defog}~\cite{mcchesney2019defog} benchmark workload performance on the edge versus on the cloud.

We contribute to this body of work by providing the first tool for the benchmarking of \gls{WCA} that dynamically considers the effects of human behavior.
In contrast to the above described works, which generate loads with relatively static profiles, our model is able to react to changes in system responsiveness like a human would.
We achieve this by building upon our own previous contributions to this field.
In~\cite{olguin2018scaling,olguin2019edgedroid} we introduced a coarse approximation to human behavior modeling in \gls{WCA} we called \emph{EdgeDroid}.
We used a trace-driven approach, where a pre-recorded and pre-processed ``ideal'' trace of steps for a specific \gls{WCA} step-based task is replayed to a Gabriel~\cite{Chen2018application} backend.
In order to adapt to potential mismatches between system responsiveness at trace-capture time and trace-replay time, we used a simple \gls{FSM} to adapt the trace at the latter by replaying or skipping certain segments.
In~\cite{olguinmunoz:impact2021} we studied the effects of reduced system responsiveness on human behavior in \gls{WCA} applications through human-subject studies.
We found that humans generally pace themselves according to the perceived system responsiveness.
When interacting with a highly responsive system, humans tended to speed up with each step; conversely, humans tended to slow down in highly unresponsive states.

The characterization and optimization of mobile \gls{XR} has also long been a topic of research.
\textcite{srinivasan2009performance} analyze a \gls{MAR} workload and identify and characterize the computational bottlenecks in the application.
They use this characterization to develop a series of code optimizations which allow them to achieve a threefold increase in performance.
\textcite{Wang2019Towards} develop a taxonomy for \gls{WCA} as well as strategies for workload reduction in these applications, including a novel adaptive sampling scheme with the goal of reducing the number of processed samples while maintaining application responsiveness.
\textcite{huang2021proactive} present a framework for the proactive allocation of edge cloud resources while taking into account the inherent mobility of wearable and mobile \gls{AR}.
\textcite{al2017energy} propose a resource allocation strategy which leverages collaboration between \gls{AR} applications to minimize energy consumption.
As above, we have also previously directly contributed to this field.
In~\cite{Moothedath2021EnergyOptimal,Moothedath2022EnergyEfficient} we find the optimum periodic sampling interval which minimizes the energy tracking human progress of a specific subtask in \gls{WCA}.
This is extended into an aperiodic strategy in~\cite{Moothedath2022Aperiodic}.
We further develop this approach in this work by deriving a more practical approximate solution to the aperiodic strategy, which we then use to implement a novel framework for the generic optimization of responsiveness-resource consumption trade-offs.

>>>>

There exist a number of approaches to the characterization and benchmarking of mobile \gls{XR}, and by extension \gls{WCA}, deployments.
\emph{OpenRTiST}~\cite{george2020openrtist} is a tool which uses a compute-heavy, yet latency-sensitive workload --- image style transfer~\cite{jing2019neural} --- to load and benchmark edge computing deployments.
It acts as an end-to-end realistic \gls{AR} workload, allowing thus researchers to measure the real end-to-end latencies of such systems.
\textcite{chen2017empirical} use a number of prototype \gls{WCA} implementation to study and characterize real-world latency bounds in these systems.
In~\cite{lecci2021open}, the authors collect and analyze large amounts of \gls{VR} network traffic, which they then use to construct a synthetic model for the generation of traces of such traffic.
\textcite{chetoui2022arbench} propose \emph{ARBench}, a toolkit for the benchmarking of mobile hardware in the context of \gls{AR}.
The toolkit incorporates a series of workloads which stress different components of the mobile device and calculates a score for each workload.
\emph{Yahoo Cloud Serving Benchmark}~\cite{cooper2010benchmarking} and \emph{DCBench}~\cite{jia2013characterizing} are workload sets intended for benchmarking cloud services which have further been used in the context of benchmarking edge computing infrastructure for \gls{AR} suitability.
\emph{Edgebench}~\cite{das2018edgebench} and \emph{Defog}~\cite{mcchesney2019defog} benchmark workload performance on the edge versus on the cloud.

We contribute to this body of work by providing the first tool for the benchmarking of \gls{WCA} that dynamically considers the effects of human behavior.
In contrast to the above described works, which generate loads with relatively static profiles, our model is able to react to changes in system responsiveness like a human would.
We achieve this by building upon our own previous contributions to this field.
In~\cite{olguinmunoz2018demoscaling,olguinmunoz2019edgedroid} we introduced a coarse approximation to human behavior modeling in \gls{WCA} we called \emph{EdgeDroid}.
We used a trace-driven approach, where a pre-recorded and pre-processed ``ideal'' trace of steps for a specific \gls{WCA} step-based task is replayed to a Gabriel~\cite{chen2018application} backend.
In order to adapt to potential mismatches between system responsiveness at trace-capture time and trace-replay time, we used a simple \gls{FSM} to adapt the trace at the latter by replaying or skipping certain segments.
In~\cite{olguinmunoz2021impact} we studied the effects of reduced system responsiveness on human behavior in \gls{WCA} applications through human-subject studies.
We found that humans generally pace themselves according to the perceived system responsiveness.
When interacting with a highly responsive system, humans tended to speed up with each step; conversely, humans tended to slow down in highly unresponsive states.

The characterization and optimization of mobile \gls{XR} has also long been a topic of research.
\textcite{srinivasan2009performance} analyze a \gls{MAR} workload and identify and characterize the computational bottlenecks in the application.
They use this characterization to develop a series of code optimizations which allow them to achieve a threefold increase in performance.
\textcite{wang2019towards} develop a taxonomy for \gls{WCA} as well as strategies for workload reduction in these applications, including a novel adaptive sampling scheme with the goal of reducing the number of processed samples while maintaining application responsiveness.
\textcite{huang2021proactive} present a framework for the proactive allocation of edge cloud resources while taking into account the inherent mobility of wearable and mobile \gls{AR}.
\textcite{al_shuwaili2017energy} propose a resource allocation strategy which leverages collaboration between \gls{AR} applications to minimize energy consumption.
As above, we have also previously directly contributed to this field.
In~\cite{moothedath2021energy,moothedath2022energy1} we find the optimum periodic sampling interval which minimizes the energy tracking human progress of a specific subtask in \gls{WCA}.
This is extended into an aperiodic strategy in~\cite{moothedath2022energy2}.
We further develop this approach in this work by deriving a more practical approximate solution to the aperiodic strategy, which we then use to implement a novel framework for the generic optimization of responsiveness-resource consumption trade-offs.
